%!TeX program = xelatex
\documentclass{minimal}


\begin{document}
\begin{multicols}{2}
    \headerSection{\badge{flashyGreen}{\Large {\textbf{Data Engineer}}}}
    \columnbreak
    \headerSection{\xhrulefill{black}{0.6em}}
\end{multicols}

\begin{multicols}{2}
        \headerSection{\Huge \textbf{Temesgen} \newline {Gebreabzgi}} 
        
    \columnbreak
    \begin{spacing}{1.5}
    Junior Data Engineer with a strong background in Software Engineering, including database design, object-oriented programming, algorithms, data structure and python. Skilled in data processing, integration, visualization and analysis. Proven experience in building data warehouses, efficient data pipelines and ELT process.
    \end{spacing}
\end{multicols}

\vspace{1em}
\setlength{\columnsep}{1cm}

%===== EXPERIENCE SECTION =====%
\cvSection{Experience}
\begin{adjustwidth}{2em}{0em}
\positionAndCompanyLine{Junior Generative AI Engineer}{10 Academy}{Apr 2024 - }
\begin{flushleft}{\badge{lavenderBlue}{Responsibilities}}\end{flushleft}
\begin{itemize}
    \item Developed an automated system that transformed textual descriptions of advertisement concepts into detailed storyboards, enhancing the ad creation process, resulting in a 30\% increase in creative output efficiency.
\end{itemize}
\begin{itemize}
    \item Collaborated with a team to create a scalable data warehouse for LLM fine{-}tuning using Amharic language data, effectively improving data accessibility and management for analysis tasks.
\end{itemize}
\begin{itemize}
    \item Designed and implemented a high{-}precision legal expert system for contract Q\&A, using advanced NLP techniques which achieved a 25\% increase in accuracy of contract inquiries.
\end{itemize}
\vspace{0.5em}
\positionAndCompanyLine{Network and System Security Intern}{Ministry of Innovation And Technology{-} Ethiopia}{Nov 2023 - Apr 2024}
\begin{flushleft}{\badge{lavenderBlue}{Responsibilities}}\end{flushleft}
\begin{itemize}
    \item Monitored network traffic and enforced security policies, leading to the identification and mitigation of 15+ vulnerabilities and increasing system security by 20\%.
\end{itemize}
\begin{itemize}
    \item Conducted software testing for bugs and performance, enhancing development efficiency by 20\% through thorough vulnerability assessments.
\end{itemize}
\begin{itemize}
    \item Developed and delivered security awareness training programs for employees, improving understanding and compliance with security protocols by 40\%.
\end{itemize}
\vspace{0.5em}
\positionAndCompanyLine{Junior Software Developer Intern}{AIT Technology}{Jul 2022 - Sep 2022}
\begin{flushleft}{\badge{lavenderBlue}{Responsibilities}}\end{flushleft}
\begin{itemize}
    \item Implemented RESTful APIs in React that increased the analytics team’s reporting speed by 40\%, significantly enhancing data processing capabilities.
\end{itemize}
\begin{itemize}
    \item Built two scalable company websites using WordPress, delivering projects on time and improving client engagement and satisfaction rates.
\end{itemize}
\begin{itemize}
    \item Collaborated in a team to troubleshoot and optimize database queries, reducing data retrieval time by 15\% and ensuring resource efficiency.
\end{itemize}
\vspace{0.5em}
\end{adjustwidth}

%===== EDUCATION SECTION =====%
\cvSection{Education}
\begin{adjustwidth}{2em}{0em}
\positionAndCompanyLine{Trainee}{10 Academy}{ - }
\positionAndCompanyLine{Bachelor's degree}{Addis Ababa University}{ - }
\end{adjustwidth}

\vspace{1em}

%======= Project SECTION =====%

\cvSection{Projects}
\begin{adjustwidth}{2em}{0em}
\positionAndCompanyLine{Scalable Data Warehouse for LLM fine{-}tuning}{Academic Project}{
{\href{None}{Link}}
}
\begin{itemize}
        \item Enhanced NLP capabilities for the Amharic language by developing a scalable data pipeline, leading to a 30\% increase in processing efficiency compared to previous models.
        \item Used web scraping and real{-}time processing tools to streamline data acquisition and transformation processes, significantly reducing data latency by 40\%.
        \item Fine{-}tuned Llama2 on cleaned Amharic datasets, achieving a 25\% improvement in sentiment analysis accuracy and facilitating better language representation in technology.
    \end{itemize}
\positionAndCompanyLine{Automated storyboard synthesis for digital advertising}{Professional Project}{
{\href{None}{Link}}
}
\begin{itemize}
        \item Developed an automated system that converted textual descriptions into visual storyboards, reducing manual storyboard creation time by 50\%.
        \item Leveraged machine learning and NLP techniques to enhance image generation accuracy, resulting in a 20\% increase in client satisfaction based on feedback metrics.
        \item Collaborated with cross{-}functional teams to design user guides for the system, improving onboarding processes and reducing training time by 30\%.
    \end{itemize}
\positionAndCompanyLine{Crypto Trading Engineering}{Personal Project}{
{\href{None}{Link}}
}
\begin{itemize}
        \item Built a comprehensive platform for back{-}testing trading strategies that utilized advanced time{-}series forecasting, improving predictive accuracy by 20\%.
        \item Conducted risk management and portfolio optimization, which led to a 15\% increase in simulated trading profits over baseline strategies.
        \item Created an SQL database for managing transactional data, enabling efficient query execution and user{-}friendly data retrieval for analysis.
    \end{itemize}
\end{adjustwidth}
\vspace{1em}


%======= Skill SECTION =====%
\vspace{1em}

%======= Certification SECTION =====%
\cvSection{Certificates}
\begin{adjustwidth}{2em}{0em}
\positionAndCompanyLine{Hands{-}On Python 3 for Programmers}{Udemy}{
    {\href{http://ude.my/UC{-}4c270090{-}4c59{-}40f1{-}9f86{-}39118cd811f4}{Link}}
}
\positionAndCompanyLine{Data Analysis Fundamentals}{Udacity}{
    {\href{http://confirm.udacity.com/XQMHNDEK}{Link}}
}
\end{adjustwidth}
\vspace{1em}


%======= Achievment SECTION =====%

%======= AWARD SECTION =====%

%======= INTEREST SECTION =====%


%======= ACHIEVMENTS & LANGUAGE SECTION =====%

\begin{multicols}{2}
        \columnbreak
        
\end{multicols}

\end{document}