\documentclass[10pt, A4]{classic}

\begin{document}

%===== TITLE SECTION =====%
\begin{center}
    {\HUGE\textsc{Temesgen Gebreabzgi}} \textcolor{sectcol}{\rule[-1mm]{1mm}{0.9cm}} \textsc{Data Engineer}\\[2pt]
\end{center}

%===== Information SECTION =====%

        
        
        
        \metasection{\href{https://www.linkedin.com/in/temesgen{-}gebreabzgi/}{https://www.linkedin.com/in/temesgen{-}gebreabzgi/}}
    

\vspace{-2pt}
\textcolor{softcol}{\hrule}
\vspace{6pt}

\normalsize

%===== Professional Summary =====%
\cvsection{Professional Summary}
\begin{highlights}
    \item {Ambitious Data Engineer with a Bachelor of Science in Information Systems from Addis Ababa University. Experienced in data science, software development, and data engineering techniques. Skilled in developing toolkits, templates, and user guides for data management tools. Adept at centralizing and organizing data, conducting research, and presenting findings to support decision{-}making.}
\end{highlights}

%===== EXPERIENCE SECTION =====%
\cvsection{Experience}
        \cvevent{Apr 2024 - }{Junior Generative AI Engineer}{10 Academy}
        
    \begin{highlights}
            \item {Developed an automated system that transformed textual descriptions of advertisement concepts into detailed storyboards, enhancing the ad creation process, resulting in a 30\% increase in creative output efficiency.}
            \item {Collaborated with a team to create a scalable data warehouse for LLM fine{-}tuning using Amharic language data, effectively improving data accessibility and management for analysis tasks.}
            \item {Designed and implemented a high{-}precision legal expert system for contract Q\&A, using advanced NLP techniques which achieved a 25\% increase in accuracy of contract inquiries.}
        \end{highlights}
        \cvevent{Nov 2023 - Apr 2024}{Network and System Security Intern}{Ministry of Innovation And Technology{-} Ethiopia}
        
    \begin{highlights}
            \item {Monitored network traffic and enforced security policies, leading to the identification and mitigation of 15+ vulnerabilities and increasing system security by 20\%.}
            \item {Conducted software testing for bugs and performance, enhancing development efficiency by 20\% through thorough vulnerability assessments.}
            \item {Developed and delivered security awareness training programs for employees, improving understanding and compliance with security protocols by 40\%.}
        \end{highlights}
        \cvevent{Jul 2022 - Sep 2022}{Junior Software Developer Intern}{AIT Technology}
        
    \begin{highlights}
            \item {Implemented RESTful APIs in React that increased the analytics team’s reporting speed by 40\%, significantly enhancing data processing capabilities.}
            \item {Built two scalable company websites using WordPress, delivering projects on time and improving client engagement and satisfaction rates.}
            \item {Collaborated in a team to troubleshoot and optimize database queries, reducing data retrieval time by 15\% and ensuring resource efficiency.}
        \end{highlights}

%===== EDUCATION SECTION =====%
\cvsection{Education}
        \cvevent{April 2024 - September 2024}{Trainee}{10 Academy}
        
        
            \cvevent{December 2019 - December 2023}{Bachelor's degree}{Addis Ababa University}
        
        
    
%===== SKILLS SECTION =====%

%===== PROJECTS SECTION =====%
\cvsection{Projects}
    \cvevent{\href{None}{Project Link}}{Scalable Data Warehouse for LLM fine{-}tuning}{Academic Project}
    \begin{highlights}
            \item Enhanced NLP capabilities for the Amharic language by developing a scalable data pipeline, leading to a 30\% increase in processing efficiency compared to previous models.
            \item Used web scraping and real{-}time processing tools to streamline data acquisition and transformation processes, significantly reducing data latency by 40\%.
            \item Fine{-}tuned Llama2 on cleaned Amharic datasets, achieving a 25\% improvement in sentiment analysis accuracy and facilitating better language representation in technology.
        \end{highlights}
    \cvevent{\href{None}{Project Link}}{Automated storyboard synthesis for digital advertising}{Professional Project}
    \begin{highlights}
            \item Developed an automated system that converted textual descriptions into visual storyboards, reducing manual storyboard creation time by 50\%.
            \item Leveraged machine learning and NLP techniques to enhance image generation accuracy, resulting in a 20\% increase in client satisfaction based on feedback metrics.
            \item Collaborated with cross{-}functional teams to design user guides for the system, improving onboarding processes and reducing training time by 30\%.
        \end{highlights}
    \cvevent{\href{None}{Project Link}}{Crypto Trading Engineering}{Personal Project}
    \begin{highlights}
            \item Built a comprehensive platform for back{-}testing trading strategies that utilized advanced time{-}series forecasting, improving predictive accuracy by 20\%.
            \item Conducted risk management and portfolio optimization, which led to a 15\% increase in simulated trading profits over baseline strategies.
            \item Created an SQL database for managing transactional data, enabling efficient query execution and user{-}friendly data retrieval for analysis.
        \end{highlights}

%===== CERTIFICATES SECTION =====%
\cvsection{Certificates}
    \cvevent{\href{http://ude.my/UC{-}4c270090{-}4c59{-}40f1{-}9f86{-}39118cd811f4}{link}}{Hands{-}On Python 3 for Programmers}{Udemy}
    \cvevent{\href{http://confirm.udacity.com/XQMHNDEK}{link}}{Data Analysis Fundamentals}{Udacity}

%===== KEYWORDS SECTION =====%

%======= AWARD SECTION =====%

%======= INTEREST SECTION =====%

% ==== LANGUAGE SECTION =====%

\end{document}